---
title: "DT Play"
author: "Niraj Juneja"
date: "8/30/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny.  Made as playground for lwarnign the DT package

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## DT Table playground
Play with DT

```{r dt-plan , echo=FALSE , message=FALSE}
library(DT)
iris2 = head(iris, 20)
options(DT.options = list(pageLength = 5))
# default Bootstrap style in DT
#datatable(iris2, style = 'bootstrap')

datatable(head(iris), colnames = c('Here', 'Are', 'Some', 'New', 'Names'))

datatable(iris2,  colnames = c('Here', 'Are', 'Some', 'New', 'Names') ,
          style = 'bootstrap', class = 'table-bordered')


```

```{r}
m = matrix(c(
  '<b>Bold</b>', '<em>Emphasize</em>', '<a href="http://rstudio.com">RStudio</a>',
  '<a href="#" onclick="alert(\'Hello World\');">Hello</a>'
), 2)
colnames(m) = c('<span style="color:red">Column 1</span>', '<em>Column 2</em>')
datatable(m , escape = FALSE)  # escape = TRUE by default
```



```{r}
library(shiny)



A <- c("Alpha", "Beta", "Gamma", "Delta")
B <- c("one","two","three","four")
C <- c("five","six","seven","eight")


Test_File <- tibble::tibble("A" = A , "B" = B , "C" = C)

renderDataTable(
  data <- Test_File %>%
      dplyr::select(A,B) %>%
      dplyr::mutate(URL = paste0("https://www.testsite.com/abcdefg/", A))%>%
      dplyr::mutate(URL = paste0("<a href='", URL, "'>",A,"</a>"))
  , escape = FALSE)


```


## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



